### 2017-09-30 Gruba/01-intro.tex
v2.1
v2.1

\section{\textcolor{red}{Introduction}}
\label{sec:intro}

\begin{comment}
\textbf{Motivation}

\textbf{Example}

\textbf{Challenge}

\textbf{Contribution}

\textcolor{blue}{organization of the sections}

%This section shall look into the principle of each component in Processing Runtime subsystem, putting forth a full-fledged system.

\end{comment}

%zhu begin

The rapid development of social network is accompanied by the generation of tremendous user-generated contents. People not only consume information but also publish or share messages. An interesting function in many existing Social Network Applications is reposting (e.g, reposting someone else's microblog on weibo.com). Modeling reposting behavior is of vital significance for Social Network Applications, which can help them to mine potential benefits, predict bursting events and so on. \par

Modeling reposting behavior has attracted attention from both academia and industry. However, many existing works have certain limitations. First, most of them mainly studied how to model reposting behavior for a single user or for the whole users. Considering the huge amount of users in Social Network , modeling for a single user is not easy. What's more, it can also make our model too particular. Modeling for the whole users is also not a good idea, which may get a inaccuracy model. Secondly, how to extract users's features, especially the extraction of users's interest, is a challenging problem.\par
To this end, we extract each user's features firstly, including user's basic information, behavior information and interests, then perform users clustering to divide users into groups and model reposting behavior of each user group respectively. The main contributions of this work can be summarized as follows:\par
\begin{itemize}
\item   We construct a large collection of microblogs from a real microblog service. It contains users's information, microblog content and part of the social network information of related users.
\item   Instead of modeling for a single user or the whole users, we divide all users into several groups by users clustering and model for each group.
\item	We propose a noval method to extract user interests from user generated texts.
\item	We develop a demo system for visualization of single user's profiling and each group's information.
\end{itemize}

This article is organized as follows: In Section 2, we introduce the framework of our work. We then describe our methodology in section 3, including features extraction, how we cluster users into groups, and how to model reposting behavior. Section 4 presents and discusses the experimental results. Section 5 discusses related work followed by conclusions in Section 6.\par

>>>>

\section{Introduction}
\label{sec:intro}

Social media is overwhelming nowadays, with massive users on Facebook \refe{}, Twitter \refe{} and Weibo \refe{} while the number of users keeps increasing.
These users behave variously, knowledge of which is significant in recommendation system, activity prediction and Big Thing analysis.
Hence emerges the demand of developing systems and algorithms that could properly model user behaviors, which has attracted the attention from both academia and industry.

Central to user behavior modeling, is the need to choose the unit of model (i.e., how many users share one model), as well as the variety of features to be selected for differentiating these units.
Already, there exist work of building a single model for all the users \refe{}.
Apparently, such model bears the limitation of being coarse.
On the other hand, modeling each user is not practical, due to the tremendous number of users.

The key driver of our work is the realization that in social media applications, users could fall into groups and each group shares representative behaviors.
Particularly, we study the \retg{} behavior of users and our work can be generalized to other behaviors of like and comment as well. 
As one example, consider the film \textit{Brave Heart}, fans of which are probably addicted to highland, bagpipe and war films, and thus likely to \ret{} blogs of these topics.

The contributions of this work include:
\begin{itemize}
\item We present a system named \sys{} with the novel perspective to model user behaviors over groups instead of the mono model in literature.
\item We leverage user interests to facilitate the modeling of \retg{} behavior and look into interests with various dimensions, including long-term/recent interests and explicit/implicit interests.
\item We evaluate the performance of \sys{} using real-world datasets, showcasing its benefits against competitive state of the art approaches.
\end{itemize}

The rest of this paper is organized as follows.
Section \ref{sec:overv} first gives the problem formulation and subsequently overviews \sys{}'s components, principle of which are detailed in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
Section \ref{sec:perf} provides the performance evaluation.
Related work is presented in Section \ref{sec:rela}.
Finally, Section \ref{sec:conclu} concludes the work.
